Structured Versus Decorated Cospans

### 2021-06-28 cospans_new.tex
removed "better" from Acknowledgements
fixed the stuff about I_a in paragraph 2 of proof of Thm. 4.1

We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations.  We especially thank Michael Shulman for suggesting a better proof strategy that greatly improved this paper.  The third author would like to thank the General Secretariat for Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).

@@

By \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$. Diagrammatically,
\[
 F\maps\A\to\Cat\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
\]
describes the construction of the adjunction from the original $F$. Explicitly, the left adjoint maps each object $a \in \A$ to the initial object in its fiber $\X_a$, namely $L(a)=(a,\bot_a)$, which is expressed as $F(!_a)\circ\phi_0(*)$ according to \cref{eq:explicitstructure1}, where $(\phi,\phi_0)$ the lax monoidal structure of $F$.

@@

Given the hypothesis of \cref{thm:equiv}, the isomorphism $\Fr(F)$ between decorated and 
structured cospans works as follows.  First recall that $\X = \inta F$, so that an object of $\X$ is a pair $(a,s)$ with $a \in \A$ and $s \in F(a)$.   The functor $U \maps \X \to \A$ maps $(a,s)$ to $a$.    Its left adjoint $L \maps \A \to \X$ maps $a \in \A$ to $(a,I_a)$, where $I_a \in F(a)$ is the \define{trivial decoration} given by the composite
\[  \one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a). \]
The object $L(a) = (a,I_a)$ is the initial object in the fiber of $\inta F$ over $a$.

>>>>

We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations.  We especially thank Michael Shulman for suggesting a proof strategy that greatly improved this paper.  The third author would like to thank the General Secretariat for Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).

@@

By \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$. Diagrammatically,
\[
 F\maps\A\to\Cat\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
\]
describes the construction of the adjunction from the original $F$. Explicitly, the left adjoint maps each object $a \in \A$ to the initial object in its fiber $\X_a$, namely $L(a)=(a,I_a)$, where $I_a$ is defined as in \cref{eq:explicitstructure1}.

@@

Given the hypothesis of \cref{thm:equiv}, the isomorphism $\Fr(F)$ between decorated and 
structured cospans works concretely as follows.  First recall that $\X = \inta F$, so that an object of $\X$ is a pair $(a,s)$ with $a \in \A$ and $s \in F(a)$.   The functor $U \maps \X \to \A$ maps $(a,s)$ to $a$.    Its left adjoint $L \maps \A \to \X$ maps $a \in \A$ to $(a,I_a)$, where $I_a \in F(a)$ is the \define{trivial decoration} given by the composite
\[  \one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a). \]
The object $L(a) = (a,I_a)$ is the initial object in the fiber of $\inta F$ over $a$.
